Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-06-09 manuscript/manuscript.tex
modify the code readme and include the new test about ambiguity in the manuscript

A considerable amount of literature has been published on the magnetic
modelling of uniformly magnetized ellipsoids since the second half of
the nineteenth century. Ellipsoids have flexibility to represent a wide
range of geometrical forms, are the only known bodies which can be
uniformly magnetized in the presence of a uniform inducing field and
are the only finite bodies for which the self-demagnetization can be treated
analytically. This property makes ellipsoids particularly useful for
modelling compact orebodies having high susceptibility. In this case,
neglecting the self-demagnetization may strongly mislead the interpretation
of these bodies by using magnetic methods. A number of previous studies
consider that the self-demagnetization can be neglected for the case in
which the geological body has an isotropic susceptibility lower than or
equal to 0.1 SI. This limiting value, however, seems to be determined
empirically and there has been no discussion about how this value was
determined. Besides, the geoscientific community lacks an easy-to-use
tool to simulate the magnetic field produced by uniformly magnetized
ellipsoids. Here, we present an integrated review of the magnetic
modelling of arbitrarily oriented triaxial, prolate and oblate
ellipsoids. Our review includes ellipsoids with both induced and
remanent magnetization, as well as with isotropic or anisotropic
susceptibility. We also propose a
way of determining the isotropic susceptibility above which the
self-demagnetization must be taken into consideration. Tests with
synthetic data validate our approach. Finally, we provide a set
of routines to model the magnetic field produced
by ellipsoids. The routines are written in Python language as
part of the Fatiando a Terra, which is an open-source library
for modelling and inversion in geophysics.

@@

There is a fundamental non-uniqueness of ellipsoidal bodies, analogous to the
equivalence of concentric spheres with the same magnetic moment.
To show this ambiguity, let us first
consider an ellipsoid which is immersed in a uniform inducing
field and has semi-axes $a$, $b$, and $c$, isotropic susceptibility $\chi$
and no remanence.
The magnetization of this ellipsoid, defined in the local coordinate system,
can be obtained by using Eqs. \ref{eq:K-isotropic}, \ref{eq:H-tilde}, and \ref{eq:M-tilde}
as follows:
\begin{equation}
\tilde{\mathbf{M}} = \chi \left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} 
\right)^{-1} \tilde{\mathbf{H}}_{0} \: .
\label{eq:M-tilde-K-isotropic}
\end{equation}
In this case, the magnetic moment $\tilde{\mathbf{P}}$, defined in the
local coordinate system, is given by
\begin{equation}
\tilde{\mathbf{P}} = \vartheta \tilde{\mathbf{M}} \: ,
\label{eq:P-tilde}
\end{equation}
where $\vartheta = \frac{4}{3}\pi a b c$ is the ellipsoid volume.
From Eqs. \ref{eq:M-tilde-K-isotropic} and \ref{eq:P-tilde},
we can easily show that, if the inducing field $\tilde{\mathbf{H}}_{0}$
is parallel to a semi-axis $e_{i}$, where $i = 1, 2, 3$, $e_{1} = a$, $e_{2} = b$,
$e_{3} = c$, only the $i$th component $P_{i}$ of the magnetic moment $\tilde{\mathbf{P}}$
is non null and given by
\begin{equation}
P_{i} = \vartheta \frac{\chi \, H_{0}}{1 + \chi \, \tilde{n}^{\dagger}_{ii}} \: ,
\label{eq:P-tilde-i}
\end{equation}
where $H_{0}$ is the intensity of the inducing field $\tilde{\mathbf{H}}_{0}$
and the demagnetizing factor $\tilde{n}^{\dagger}_{ii}$ is defined
by Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.

Now, consider a confocal ellipsoid with semi-axes $a^{\prime} = \sqrt{a^2+u}$,
$b^{\prime} = \sqrt{b^2+u}$, and $c^{\prime} = \sqrt{c^2+u}$, where $u$ is a
positive real number. From Eq. \ref{eq:P-tilde-i}, we can define the
isotropic susceptibility $\chi^{\prime}$ that is necessary to this confocal
ellipsoid produce the same magnetic moment $\tilde{\mathbf{P}}$ (Eq. \ref{eq:P-tilde})
as follows:
\begin{equation}
\chi^{\prime} = \frac{P_{i}}{\vartheta^{\prime} \, H_{0} - \tilde{n}^{\dagger}_{ii} \, P_{i}} \: ,
\label{eq:chi-prime}
\end{equation}
where $\vartheta^{\prime} = \frac{4}{3}\pi a^{\prime} b^{\prime} c^{\prime}$ and
$\tilde{n}^{\dagger}_{ii}$ is the new demagnetizing factor computed for the
confocal ellipsoid by using Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.
It can be shown that this confocal ellipsoid produce the same magnetic field
as the ellipsoid with semi-axes $a$, $b$, and $c$.

This ambiguity between confocal ellipsoids with the same magnetic moment
has already been pointed out by Clark (2014) and is verified for the
particular case in which the uniform inducing field is parallel
to an ellipsoid axis.
Otherwise, the magnetic field produced by the confocal ellipsoids
will be different due to the shape anisotropy.

@@

We simulate a triaxial ellipsoid with semi-axes
$a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m}, and $c_{0} = 200$ \unit{m}.
Then we use this ellipsoid as a reference to generate
100 different triaxial ellipsoids and calculate
their demagnetizing factors $\tilde{n}^{\dagger}_{11}$,
$\tilde{n}^{\dagger}_{22}$, and $\tilde{n}^{\dagger}_{33}$
by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
The semi-axes of these 100 ellipsoids are given by
$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and
$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$.
Notice that, for $u = 0$, the resulting semi-axes are equal those
of the reference ellipsoid.
The larger the variable $u$, the larger the resulting semi-axes
$a$, $b$, and $c$, but the smaller the relative difference between
them.
Consequently, the resulting ellipsoids obtained from the semi-axes
$a$, $b$, and $c$ become more spherical as $u$ increases.
In this case, the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}),
$\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-triaxial}),
and
$\tilde{n}^{\dagger}_{33}$ (Eq. \ref{eq:n-tilde-dagger-33-triaxial})
tend to $1/3$ \citep[e.g.,][]{stoner1945}.

@@

@@

We present an integrated review of the vast literature
about the magnetic modelling of triaxial, prolate and
oblate ellipsoids.
We also present a theoretical discussion about the
determination of the isotropic susceptibility value above which
the self-demagnetization must be taken into consideration.
We propose an alternative way of determining this value
based on the body shape and the maximum relative error
allowed in the resultant magnetization.
Our approach is an alternative to the constant value which
seems to be determined empirically and
has been used by the geoscientific community.
Our alternative approach is validated
by the results obtained with numerical simulations.
In a future work,
it would be interesting to use a similar approach
to determine bounds for the maximum relative error in the
magnetic field calculated by neglecting the self-demagnetization.

@@

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
\caption{Total-field anomaly produced by the synthetic orebody
defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
are calculated on a regular grid of $100 \times 100$ points
at the constant vertical coordinate $z = 0$ \unit{m}.}
\label{fig:tfa-warrego}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/field_differences.pdf}
\caption{Difference between the total-field
anomaly calculated with the approximated magnetization $\breve{\mathbf{M}}$
(Eq. \ref{eq:M-approx}) and with the
true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
The total-field anomalies are calculated with Eq. \ref{eq:delta-T-approx},
on a regular grid of $100 \times 100$ points,
at the constant vertical coordinate $z = 0$ \unit{m}.
The differences are produced by the synthetic orebody defined in
Tab. \ref{tab:parameters-warrego}, but with different
isotropic susceptibilities:
(a) the isotropic susceptibility defined in
Tab. \ref{tab:parameters-warrego},
(b) an isotropic susceptibility $\chi = 0.1$ \unit{SI}, and
(c) an isotropic susceptibility $\chi = 0.116$ \unit{SI}.
This last value was calculated
with Eq. \ref{eq:chi-max}, by using $\epsilon = 8 \%$.}
\label{fig:tfa-differences-warrego}
\end{figure}

@@

>>>>

A considerable amount of literature has been published on the magnetic
modelling of uniformly magnetized ellipsoids since the second half of
the nineteenth century. Ellipsoids have flexibility to represent a wide
range of geometrical forms, are the only known bodies which can be
uniformly magnetized in the presence of a uniform inducing field and
are the only finite bodies for which the self-demagnetization can be treated
analytically. This property makes ellipsoids particularly useful for
modelling compact orebodies having high susceptibility. In this case,
neglecting the self-demagnetization may strongly mislead the interpretation
of these bodies by using magnetic methods. A number of previous studies
consider that the self-demagnetization can be neglected for the case in
which the geological body has an isotropic susceptibility lower than or
equal to 0.1 SI. This limiting value, however, seems to be determined
empirically and there has been no discussion about how this value was
determined. Besides, the geoscientific community lacks an easy-to-use
tool to simulate the magnetic field produced by uniformly magnetized
ellipsoids. Here, we present an integrated review of the magnetic
modelling of arbitrarily oriented triaxial, prolate and oblate
ellipsoids. Our review includes ellipsoids with both induced and
remanent magnetization, as well as with isotropic or anisotropic
susceptibility. We also discuss the ambiguity between confocal ellipsoids
with the same magnetic moment and propose a
way of determining the isotropic susceptibility above which the
self-demagnetization must be taken into consideration. Tests with
synthetic data validate our approach. Finally, we provide a set
of routines to model the magnetic field produced
by ellipsoids. The routines are written in Python language as
part of the Fatiando a Terra, which is an open-source library
for modelling and inversion in geophysics.

@@

There is a fundamental non-uniqueness of ellipsoidal bodies, analogous to the
equivalence of concentric spheres with the same magnetic moment.
To show this ambiguity, let us first
consider a reference ellipsoid which is immersed in a uniform inducing
field and has semi-axes $a$, $b$, and $c$, isotropic susceptibility $\chi$
and no remanence.
The magnetization of this ellipsoid, defined in the local coordinate system,
can be obtained by using Eqs. \ref{eq:K-isotropic}, \ref{eq:H-tilde}, and \ref{eq:M-tilde}
as follows:
\begin{equation}
\tilde{\mathbf{M}} = \chi \left( \mathbf{I} + \chi \, \tilde{\mathbf{N}}^{\dagger} 
\right)^{-1} \tilde{\mathbf{H}}_{0} \: .
\label{eq:M-tilde-K-isotropic}
\end{equation}
In this case, the magnetic moment $\tilde{\mathbf{P}}$, defined in the
local coordinate system, is given by
\begin{equation}
\tilde{\mathbf{P}} = \vartheta \tilde{\mathbf{M}} \: ,
\label{eq:P-tilde}
\end{equation}
where $\vartheta = \frac{4}{3}\pi a b c$ is the ellipsoid volume.
From Eqs. \ref{eq:M-tilde-K-isotropic} and \ref{eq:P-tilde},
we can easily show that, if the inducing field $\tilde{\mathbf{H}}_{0}$
is parallel to a semi-axis $e_{i}$, where $i = 1, 2, 3$, $e_{1} = a$, $e_{2} = b$,
$e_{3} = c$, only the $i$th component $P_{i}$ of the magnetic moment $\tilde{\mathbf{P}}$
is non null and given by
\begin{equation}
P_{i} = \vartheta \frac{\chi \, H_{0}}{1 + \chi \, \tilde{n}^{\dagger}_{ii}} \: ,
\label{eq:P-tilde-i}
\end{equation}
where $H_{0}$ is the intensity of the inducing field $\tilde{\mathbf{H}}_{0}$
and the demagnetizing factor $\tilde{n}^{\dagger}_{ii}$ is defined
by Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.

Now, consider a confocal ellipsoid with semi-axes $a^{\prime} = \sqrt{a^2+u}$,
$b^{\prime} = \sqrt{b^2+u}$, and $c^{\prime} = \sqrt{c^2+u}$, where $u$ is a
positive real number. From Eq. \ref{eq:P-tilde-i}, we can define the
isotropic susceptibility $\chi^{\prime}$ that is necessary to this confocal
ellipsoid produce the same magnetic moment $\tilde{\mathbf{P}}$ (Eq. \ref{eq:P-tilde})
as follows:
\begin{equation}
\chi^{\prime} = \frac{P_{i}}{\vartheta^{\prime} \, H_{0} - \tilde{n}^{\dagger}_{ii} \, P_{i}} \: ,
\label{eq:chi-prime}
\end{equation}
where $\vartheta^{\prime} = \frac{4}{3}\pi a^{\prime} b^{\prime} c^{\prime}$ and
$\tilde{n}^{\dagger}_{ii}$ is the new demagnetizing factor computed for the
confocal ellipsoid by using Eq. \ref{eq:n-tilde-dagger-11-triaxial}, \ref{eq:n-tilde-dagger-11-prolate},
or \ref{eq:n-tilde-dagger-11-oblate}, according to the ellipsoid type.
It can be shown that this confocal ellipsoid produce the same magnetic field
as the reference ellipsoid.

This ambiguity between confocal ellipsoids with the same magnetic moment
has already been pointed out by Clark (2014). It occurs for the
particular case in which the uniform inducing field is parallel
to an ellipsoid axis and there is no remanence.
Otherwise, the magnetic field produced by the confocal ellipsoids
will be different due to the shape anisotropy.

@@

We simulated a triaxial ellipsoid with semi-axes
$a_{0} = 1000$ \unit{m}, $b_{0} = 700$ \unit{m}, and $c_{0} = 200$ \unit{m}.
Then we used this ellipsoid as a reference to generate
100 different triaxial ellipsoids and calculate
their demagnetizing factors $\tilde{n}^{\dagger}_{11}$,
$\tilde{n}^{\dagger}_{22}$, and $\tilde{n}^{\dagger}_{33}$
by using Eqs. \ref{eq:n-tilde-dagger-11-triaxial},
\ref{eq:n-tilde-dagger-22-triaxial}, and \ref{eq:n-tilde-dagger-33-triaxial}.
The semi-axes of these 100 ellipsoids are given by
$a = a_{0} + u \; b_{0}$, $b = b_{0} + u \; b_{0}$, and
$c = c_{0} + u \; b_{0}$, where $0 \leq u \leq 10$.
Notice that, for $u = 0$, the resulting semi-axes are equal those
of the reference ellipsoid.
The larger the variable $u$, the larger the resulting semi-axes
$a$, $b$, and $c$, but the smaller the relative difference between
them.
Consequently, the resulting ellipsoids obtained from the semi-axes
$a$, $b$, and $c$ become more spherical as $u$ increases.
In this case, the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}),
$\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-triaxial}),
and
$\tilde{n}^{\dagger}_{33}$ (Eq. \ref{eq:n-tilde-dagger-33-triaxial})
tend to $1/3$ \citep[e.g.,][]{stoner1945}.

@@

\subsection{Confocal ellipsoids}

We simulated two confocal ellipsoids by using the parameters
shown in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The semi-axes of the Ellipsoid 2 were defined as $\sqrt{a^{2} + u}$,
$\sqrt{b^{2} + u}$, and $\sqrt{c^{2} + u}$, where $a$, $b$, and $c$
are the semi-axes of the Ellipsoid 1 and $u = 2 \times 10^{6}$ \unit{m}.

We have computed the total-field anomalies produced by the Ellipsoid 1
and Ellipsoid 2 at the same regular grid of $200 \times 200$ points
located on a horizontal plane at $z = 0$ \unit{m} by using two different
inducing fields $\mathbf{H}_{0}$.

In the first case, we used an uniform inducing field $\mathbf{H}_{0}$ which is
parallel to the semi-axis $a$ of the confocal ellipsoids and
has inclination $\approx -4.98^{\circ}$, declination $\approx 15.38^{\circ}$,
and intensity $H_{0} \approx 18.7$ \unit{A \, m^{-1}}.
The total-field anomaly produced by the Ellipsoid 1 by using this
inducing field is shown in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-parallel}.
In this case, the Ellipsoid 2 produces the same total-field
anomaly as the Ellipsoid 1.
The isotropic susceptibility of the Ellipsoid 2 was calculated with
Eq. \ref{eq:chi-prime} and, consequently, its magnetic moment is equal
to that of the Ellipsoid 1.
Notice that the volume of the Ellipsoid 2 is approximately $79$ times greater
than that of the Ellipsoid 1, whereas the isotropic susceptibility
of the Ellipsoid 1 is approximately $85$ times greater than that
of the Ellipsoid 2.
This result illustrates the ambiguity between the field produced
by confocal ellipsoids with the same magnetic moment.

The second inducing field $\mathbf{H}_{0}$ used is oblique to
the semi-axes of the confocal ellipsoids, has the same
intensity as the other one, but a different direction.
In this case, the inclination and declination of $\mathbf{H}_{0}$
are, respectively, $-30^{\circ}$ and $60^{\circ}$.
Figures \ref{fig:tfa-confocal-ellipsoids-H0-oblique}a and
\ref{fig:tfa-confocal-ellipsoids-H0-oblique}b show the total-field anomalies
produced, respectively, by the Ellipsoid 1 and Ellipsoid 2
by using this new inducing field $\mathbf{H}_{0}$.
Notice that by using this oblique inducing field, 
the total-field anomalies produced by the confocal ellipsoids
are different to each other due to the shape anisotropy.
The differences are show in Fig. \ref{fig:tfa-confocal-ellipsoids-H0-oblique}c.
These results confirm numerically what was pointed out by
\cite{clark2014}: confocal ellipsoids with
properly scaled isotropic susceptibilities, no remanence and
the same magnetic moment produce different magnetic fields at the
same external points, unless the inducing field happens to lie along one
of their axes.

@@

We present an integrated review of the vast literature
about the magnetic modelling of triaxial, prolate and
oblate ellipsoids.
We also present a numerical simulation confirming the
ambiguity between confocal ellipsoids with the same magnetic moment
and present a theoretical discussion about the
determination of the isotropic susceptibility value above which
the self-demagnetization must be taken into consideration.
We propose an alternative way of determining this value
based on the body shape and the maximum relative error
allowed in the resultant magnetization.
Our approach is an alternative to the constant value which
seems to be determined empirically and
has been used by the geoscientific community.
Our alternative approach is validated
by the results obtained with numerical simulations.
In a future work,
it would be interesting to use a similar approach
to determine bounds for the maximum relative error in the
magnetic field calculated by neglecting the self-demagnetization.

@@

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_parallel_field.pdf}
\caption{Total-field anomaly (in \unit{nT}) produced by the 
synthetic bodies Ellipsoid 1 and Ellispoid 2, both
defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The synthetic data produced by these confocal ellipsoids
were calculated on a regular grid of $200 \times 200$ points
at the constant vertical coordinate $z = 0$ \unit{m}.
These data were calculated with an uniform inducing field
parallel to the semi-axis $a$ of the confocal ellipsoids.}
\label{fig:tfa-confocal-ellipsoids-H0-parallel}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/confocal_ellipsoids_oblique_field.pdf}
\caption{Total-field anomalies (in \unit{nT}) produced by the (a) Ellipsoid 1
and (b) Ellipsoid 2, both defined in Tab. \ref{tab:parameters-confocal-ellipsoids}.
The synthetic data produced by these confocal ellipsoids
were calculated on a regular grid of $200 \times 200$ points
at the constant vertical coordinate $z = 0$ \unit{m}.
These data were calculated with an uniform inducing field
which is oblique to the semi-axes of the confocal ellipsoids.
(c) Difference between the total-field anomalies shown in
b and a.}
\label{fig:tfa-confocal-ellipsoids-H0-oblique}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/total-field_anomaly.pdf}
\caption{Total-field anomaly (in \unit{nT}) produced by the synthetic orebody
defined in Tab. \ref{tab:parameters-warrego}. The synthetic data
are calculated on a regular grid of $100 \times 100$ points
at the constant vertical coordinate $z = 0$ \unit{m}.}
\label{fig:tfa-warrego}
\end{figure}

%f
\begin{figure}[t]
\includegraphics[width=8.3cm]{figures/field_differences.pdf}
\caption{Difference between the total-field
anomaly calculated with the approximated magnetization $\breve{\mathbf{M}}$
(Eq. \ref{eq:M-approx}) and with the
true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
The total-field anomalies are in \unit{nT} and were
calculated with Eq. \ref{eq:delta-T-approx},
on a regular grid of $100 \times 100$ points,
at the constant vertical coordinate $z = 0$ \unit{m}.
The differences are produced by the synthetic orebody defined in
Tab. \ref{tab:parameters-warrego}, but with different
isotropic susceptibilities:
(a) the isotropic susceptibility defined in
Tab. \ref{tab:parameters-warrego},
(b) an isotropic susceptibility $\chi = 0.1$ \unit{SI}, and
(c) an isotropic susceptibility $\chi = 0.116$ \unit{SI}.
This last value was calculated
with Eq. \ref{eq:chi-max}, by using $\epsilon = 8 \%$.}
\label{fig:tfa-differences-warrego}
\end{figure}

@@

%t
\begin{table}[t]
\caption{Parameters defining two confocal ellipsoids.}
%\begin{tabular}{column = lcr}
\begin{tabular}{lccr}
\tophline
Parameter & Ellipsoid 1 & Ellipsoid 2 & Unit \\
\middlehline
Semi-axis $a$ & $900$ & $\approx 1676.31$ & \unit{m} \\
Semi-axis $b$ & $500$ & $1500$ & \unit{m} \\
Semi-axis $c$ & $100$ & $\approx 1417.74$ & \unit{m} \\
Coordinate of the centre $x_{c}$ & 0 & 0 & \unit{m} \\
Coordinate of the centre $y_{c}$ & 0 & 0 & \unit{m} \\
Coordinate of the centre $z_{c}$ & 1500 & 1500 & \unit{m} \\
Orientation angle $\varepsilon$ $^{\ast}$ & $45$ & $45$ & $^{\circ}$ \\
Orientation angle $\zeta$ $^{\ast}$ & $10$ & $10$ & $^{\circ}$ \\
Orientation angle $\eta$ $^{\ast}$ & $-30$ & $-30$ & $^{\circ}$ \\
Isotropic susceptibility $\chi$ & $1.2$ & $\approx 0.014$ & \unit{SI} \\
\bottomhline
\end{tabular}
\belowtable{$^{\ast}$ Defined in Fig. \ref{fig:orientation-angles}a} % Table Footnotes
\label{tab:parameters-confocal-ellipsoids}
\end{table}
